Spring haul-out behavior of seals in the Bering and Chukchi seas

### 2024-08-17 analysis/paper/London_HauloutBehavior.Rmd
typo fix Ribon to Ribbon

p <- ggplot(plot_df, aes(day,solar_hour,fill = ho_prob, color = ho_prob)) +
  geom_tile(linewidth = 0.15) +
  scico::scale_fill_scico(palette = "navia", direction = 1,
                          begin = 0.1, end = 1,
                       name = "Ribon seal haul-out probability", 
                       limits = c(0,1), breaks = c(0.25, 0.50, 0.75),
                       guide = guide_colorbar(title.position = "top", barwidth = 15,
                                              barheight = 0.5, title.hjust = 0)
  ) +
  scico::scale_color_scico(palette = "navia", direction = 1,
                           begin = 0.1, end = 1,
                           limits = c(0,1)) +
  guides(col = FALSE)

>>>>

p <- ggplot(plot_df, aes(day,solar_hour,fill = ho_prob, color = ho_prob)) +
  geom_tile(linewidth = 0.15) +
  scico::scale_fill_scico(palette = "navia", direction = 1,
                          begin = 0.1, end = 1,
                       name = "Ribbon seal haul-out probability", 
                       limits = c(0,1), breaks = c(0.25, 0.50, 0.75),
                       guide = guide_colorbar(title.position = "top", barwidth = 15,
                                              barheight = 0.5, title.hjust = 0)
  ) +
  scico::scale_color_scico(palette = "navia", direction = 1,
                           begin = 0.1, end = 1,
                           limits = c(0,1)) +
  guides(col = FALSE)
